MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites \\ Supplementary Material

### 2014-12-11 Rebuttal.tex

\documentclass[]{article}
\usepackage{graphicx}
\usepackage{color}
%opening
\title{MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites: Rebuttal}
\author{}

\begin{document}

\maketitle
We thank the reviewers for their reviews of the submitted manuscript, we have addressed the queries,  re-worked and improved the manuscript. The summary reviews had three issues, 
\begin{enumerate}
	   \item  Visualization of more datasets, particularly, the ones, as R1 has
	   mentioned with crossings at other angles.
	   \item Effects of choice of length in MetaTract generation.
	   \item Performance studies and limitations.
\end{enumerate}
We incorporated the following changes
\begin{enumerate}
	\item {Due to the manufacturing process, a vast majority of composites have bundles crossing at ~90 degree angles. With the separation factors being width, spacings and compactness of fiber bundles. These variations are well represented in our data sets. We maintain that the technique is useful and applicable to a large percentage of composite polymers. We have demonstrated the technique on three datasets, two of them are in the paper and the third is in the supplemental section due space  constraints. Getting additional datasets is time consuming.

		In dataset 1, Figure~\ref{fig:angle_bundles}f, bundles 7,10 and 6 show  bundles which  though parallel differ in angle and bundle width.It is a common example of variations in the datasets which we extract accurately.

		During additional experiments, we did apply our technique to a different class of fibers where the individual fibers are clearly visible, namely the glass-fibers. We have added the results to the supplementary section. 
		\begin{figure}
			\centering
			\includegraphics[width=0.7\linewidth]{images_pvis/clustering.pdf}
			\caption{Fiber bundles extraction}
			\label{fig:angle_bundles}
		\end{figure}}
		\item {
			As mentioned in the paper, 
			``The length and the radius parameters for the cylinders of MetaTracts decide how coarse the fiber cylinders are. These are dependent on the underlying fiber characteristic and the weaving pattern. Larger cylinders will handle noisy local orientation better as it inspects a higher number of candidate points to extend the fiber. We used 10.00 and 2.00 for length and radius (measured in grid voxel size), respectively for all tests.  
			Simpler geometry (example dataset 2) was experimentally found to handle larger cylinders better.''

			Reviewer 3 and  4, asked  about the effect of the length threshold ``$\eta$".  ``$\eta$" decides how quickly the hierarchical clustering converges. As mentioned in the paper,  experimentally 0.3 to 0.6 gave qualitatively similar results. Quantitatively in our  tests $1.2\% - 5\%$ of fibers (total number of fibers $\sim$10000)were removed, while quantitatively small, without removing these clusters are difficult to separate.
			}
			\item{
				We have added a limitation and future work section to the paper.}
\end{enumerate}

@@

As mentioned in the paper, we do not have clear tubular structures embedded in a dark contrast matrix such as in blood vessels ( Figure~\ref{fig:data-char-rebuttal} shows the data characteristics for our case.). Instead  the utility of $R_{H}$ is  to associate each grid location with a reliability measure for the local orientation as given by the  principal eigenvector. We use this orientation vector to create MetaTracts.

\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{images_pvis/Vesselness}
\caption{Left: Xray image of vasculature, middle-left: calculated vesselness of the left image, middle-right: calculated vesselness after inversion of the grey-scale map. Right image after subtracting reference from left image.}
\label{fig:Vesselness}
\end{figure}

\begin{figure}[tb]
	\centering
	%\includegraphics[width=0.5\textwidth, trim = 0mm 110mm 0mm 0mm, clip,]{images_pvis/figure1}
	\includegraphics[width=\linewidth]{images_pvis/data-char.pdf}
	\caption{Data characteristics: (a) Rendering of the data. (b) 2D slices along the X-axis and (c) 2D slice along the Z-axis. (d) Magnified region marked in green square (c). Multiple fiber bundles cross and are indistinguishable by visual inspection alone. }
	\label{fig:data-char-rebuttal}
\end{figure}

\color{red}
Q2. In the examples presented, it seems only one type of composite was studied. For instance, there is no example showing a composite with fiber bundles that cross each other at an angle $<$ 90 degrees. When two bundles are almost parallel, will the current algorithm be sufficient to separate them apart? The authors are encouraged to provide more than one fiber configurations.
\color{black}
Please see summary answer 1, also see supplemental sections.

@@

\color{red}
Q3. All clustering was done in R. The letter R is not explained.
\color{black}

A3. R is a free software environment for statistical computing and graphics.

\section{Reviewer 2}
\color{red}
I feel the background section could be improved. Why the orientation and weaving patterns of fibers indicate the strength of the material, and thus why the trouble to scan the materials, extract the fibers and visualize them. The paper gives some relatively high-level description of this but more background would be appreciated.

\color{black}
We modified the related works section.

\color{red}
  It seems to me that the extracted fibers may not be real fibers. Is this
  true? If so, how well can one trust the weaving patterns extracted based
  on the imaginary fibers? 
  \color{black}
  Answer. 
Yes, the extracted fibers cannot be mapped to real fibers. One of the goals  we  focused on was to move away from extraction of individual fibers, instead work on direct reconstruction of bundles. The design decisions adheres to extracting reliable bundles directly from the images. 
 Developing methods which can precisely compute the deviations from original bundles remains a future direction of the project. We did experiment with glass fibers (see supplemental section) where the individual fibers are clearly separated, and proved as a sanity check that the MetaTract technique does extract correct fibers.

@@

Answer.  Please look at the supplementary section on glass fibers.

\section{Reviewer 4}
\color{red}
In Section 5.1, k-means is applied to the m-dimensional space using
Euclidean distance, i.e., each dimension is considered equally important.
Is that really the case when they represent eigenvectors?

\color{black}
Answer. Belkin  and Niyogi's~\cite{Belkin01} laplacian eigenmaps embeds the high dimensional data ( represented as a graph ) into a low dimensional space where the Euclidean distance approximates the distances in higher dimension space. For such reason, Eigen embedding for dimensionality reduction has become quiet popular and has found favor in tackling a variety of problems. Empirically the K-means for orientation clustering provided us excellent results. The major orientations are limited by the inherent characteristics of our data set and this also plays a role in Laplacian embedding followed by k-means giving us such good results. A formal proof is not provided.

\color{red}
In Section 5.2, the authors mention that they remove short Meta Tracks.
How much data is thrown away here? Can examples be provided to get a
better understanding?
\color{black}
Please see summary answer 2.

\color{red}
What are the limitations of the approach? Are there data sets where the
method fails?
\color{black}
Answer. We have added a ``Limitations and future work" Section to the end of the paper. We copy it here for completeness.

### 2014-12-11 supplemental/supplementaryMaterial.tex
rebuttal update

Figure~\ref{fig:dataset1-extended} further shows how spatial context can be used to answer questions such as:  Are these bundles in contact at a particular position in the data? What is the relative orientations of the contacting bundles? These annotated bundles are occluded in the original volume and no conclusions can be made from the volume rendering. In the voxelized MetaTracts we can clearly see where and how the bundles interact.

>>>>

Figure~\ref{fig:dataset1-extended} further shows how spatial context can be used to answer questions such as:  Are these bundles in contact at a particular position in the data? What is the relative orientations of the contacting bundles? These annotated bundles are occluded in the original volume and no conclusions can be made from the volume rendering. In the voxelized MetaTracts we can clearly see where and how the bundles interact.
\subsection{Glass fibers}
Figure~\ref{fig:glass_fibers}a shows an example of glass fibers embedded in an epoxy matrix. Unlike the fibers in the other datasets (example Figure~\ref{fig:dataset3}a) the glass fibers are clearly separated from each other Figure~\ref{fig:glass_fibers}a.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{images_pvis/glass-fibers}
	\caption{MetaTracts being applied to glass fibers. (a) Scalar data consisting of glass fibers. (b) single slice, (c) Extracted MetaTracts colored mapped to direction.}
	\label{fig:glass_fibers}
	\end{figure}
